Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2016-12-19 src/local.tex
fix warnings
fig local tight
local

\begin{figure}[h]
\centering
\subfloat[]{
\label{subfloat:graph}
\input{fig-sub-graph}
}
\subfloat[]{
\label{subfloat:conflict}
\input{fig-sub-conflict}
}
\caption[]{
\label{fig:conflict}
\subref{subfloat:input} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.  
\subref{subfloat:output}
The conflict graph, the upper left vertex corresponds 
to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\end{figure}

@@

\begin{lemma}
\label{lemma:r}
If $k \geq something$ then in any connected induced graph of $G^{M^*}_M$, 
$G'= G^{M^*}_M[U]$, 
$
\frac{w(U)}{w^*(U)} 
\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$.
\end{lemma}

@@

\begin{theorem}
The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
algorithm.
\end{theorem}

@@

>>>>

\begin{figure}[ht]
\centering
\subfloat[]{
\label{subfloat:graph}
\input{fig-sub-graph}
}
\subfloat[]{
\label{subfloat:conflict}
\input{fig-sub-conflict}
}
\caption[]{
\label{fig:conflict}
\subref{subfloat:input} 
An optimal matching depicted by the dashed red edges,
and another solution depicted by the solid green edges.  
\subref{subfloat:output}
The conflict graph, the upper left vertex corresponds 
to the star that contains the vertices a,b,c.
The numbers inside the vertices corresponds to $d_i$.   
}
\end{figure}

@@

\begin{lemma}
\label{lemma:r}
If $k \geq \text{TODO}$ then in any connected induced graph of $G^{M^*}_M$, 
$G'= G^{M^*}_M[U]$, 
$
\frac{w(U)}{w^*(U)} 
\geq \frac{1}{2} + \frac{1}{2C} - \frac{1}{2C|U|}
$.
\end{lemma}

@@

\begin{theorem}
\label{theorem:local search}
The local search is ($\frac{1}{2} + \frac{1}{2c} - \varepsilon$)-approximation
algorithm.
\end{theorem}

@@

We now show that Theorem~\ref{theorem:local search} is tight.
Consider the example in Figure~\ref{fig:local search tight},
the example is for the special case when $k=11$ and $C=2$ but this example can
be generalized in a straightforward manner.
One can verify that as the graph in the example growth, 
the ratio between the optimal solution and the local search solution approaches
$\frac{3}{4}$.
\begin{figure}
\begin{center}
\caption{
\label{fig:local search tight}
A tight example for Theorem~\ref{theorem:local search}. 
The optimal solution is given by the red solid arcs while the local search
solution is given by the green, dashed arcs.
The solution can be improved by the local search algorithm only if it removes
all the edges. 
}
\input{fig-local-tight}
\end{center}
\end{figure}
